---
title: "fivbviz🏐"
author: "wehsLai"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    source_code: "https://github.com/wehsLai/fivbviz"
    orientation: rows
    vertical_layout: fill
    theme: 
      version: 5
      base_font:
        google: "Source Sans Pro"
      code_font:
        google: "Fira Mono"
---

<script src="https://cdnjs.cloudflare.com/ajax/libs/clipboard.js/2.0.10/clipboard.min.js"></script>

<style type="text/css">
#dashboard-container {
  font-size: 15px;
}

.btn, dropdown, .bttn-bordered.bttn-sm {
  font-size: 15px;
}

.form-group {
  margin-bottom: 2px;
}

.selectize-dropdown-content {
  max-height: 400px
}

.shiny-input-panel {
    padding-top: 6px;
    padding-right: 8px;
    padding-bottom: 10px;
    padding-left: 8px;
}

pre.shiny-text-output {
  white-space: pre-wrap;
}

</style>

```{r setup, include=FALSE}
options(encoding = 'UTF-8')
source("R/global.R")
source("R/data_transform.R")
source("R/chart.R")
source("R/helper.R")
source("R/mod_dataFilter.R")
source("R/mod_download.R")
source("R/mod_tournaments.R")
source("R/mod_rankBySkill.R")
source("R/mod_matches.R")
source("R/mod_roster.R")
source("R/mod_clipboard.R")
source("R/mod_clipboardP3.R")
autoWaiter()
```

# Tournament

## Control {.sidebar}

How to Use:  
1. Select Tournament → OPEN  
2. (option)Select Round → Filter

If there are players not on the roster, Team stats and Load column of Player stats will not be the correct number.

```{r message=FALSE, warning=FALSE}
inputPanel(
dataFilterUI("filter")
)
inputPanel(
downloadUI("rds", "RDS", color = "success"),
downloadUI("dashboard", "dashboard", color = "warning"),
downloadUI("html", "html", color = "warning"),
downloadUI("p56", "p56", color = "warning"),
showRkUI("p56", "P56 All", color = "warning")
)
reactive({
  if (!is.null(rv$ds)) {
    dataFilterServer("filter", showSeason, addPoolName = TRUE)
    downloadServer("rds", type = "ds")
    downloadServer("dashboard", type = "dashboard")
    downloadServer("html", type = "html")
    downloadServer("p56", type = "p56")
  }
})
```

## Row

### Tournaments

```{r message=FALSE, warning=FALSE}
tournamentsUI("tournaments")
showSeason <- showSeasonVal("tournaments")
tournamentsServer("tournaments", showSeason)
```

# Player Charts

## Row {.tabset}

### Score

```{r message=FALSE, warning=FALSE}
rankBySkillUI("scorer")
observe({
  if (!is.null(rv$fds$statistics$player_agg) && nrow(rv$fds$statistics$player_agg) > 0) {
    type <- "c"
    isTeam <- FALSE
    f <- rankBySkillDfServer("scorer", rv$fds$statistics$player_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("scorer", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("scorer", f, type = type, isTeam = isTeam)
  }
})
```

### Attack

```{r message=FALSE, warning=FALSE}
rankBySkillUI("attacker")
observe({
  if (!is.null(rv$fds$statistics$player_agg) && nrow(rv$fds$statistics$player_agg) > 0) {
    type <- "a"
    isTeam <- FALSE
    f <- rankBySkillDfServer("attacker", rv$fds$statistics$player_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("attacker", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("attacker", f, type = type, isTeam = isTeam)
  }
})
```

### Block

```{r message=FALSE, warning=FALSE}
rankBySkillUI("blocker")
observe({
  if (!is.null(rv$fds$statistics$player_agg) && nrow(rv$fds$statistics$player_agg) > 0) {
    type <- "b"
    isTeam <- FALSE
    f <- rankBySkillDfServer("blocker", rv$fds$statistics$player_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("blocker", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("blocker", f, type = type, isTeam = isTeam)
  }
})
```

### Serve

```{r message=FALSE, warning=FALSE}
rankBySkillUI("server")
observe({
  if (!is.null(rv$fds$statistics$player_agg) && nrow(rv$fds$statistics$player_agg) > 0) {
    type <- "s"
    isTeam <- FALSE
    f <- rankBySkillDfServer("server", rv$fds$statistics$player_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("server", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("server", f, type = type, isTeam = isTeam)
  }
})
```

### Dig

```{r message=FALSE, warning=FALSE}
rankBySkillUI("digger")
observe({
  if (!is.null(rv$fds$statistics$player_agg) && nrow(rv$fds$statistics$player_agg) > 0) {
    type <- "d"
    isTeam <- FALSE
    f <- rankBySkillDfServer("digger", rv$fds$statistics$player_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("digger", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("digger", f, type = type, isTeam = isTeam)
  }
})
```

### Set

```{r message=FALSE, warning=FALSE}
rankBySkillUI("setter")
observe({
  if (!is.null(rv$fds$statistics$player_agg) && nrow(rv$fds$statistics$player_agg) > 0) {
    type <- "e"
    isTeam <- FALSE
    f <- rankBySkillDfServer("setter", rv$fds$statistics$player_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("setter", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("setter", f, type = type, isTeam = isTeam)
  }
})
```

### Receive

```{r message=FALSE, warning=FALSE}
rankBySkillUI("receiver")
observe({
  if (!is.null(rv$fds$statistics$player_agg) && nrow(rv$fds$statistics$player_agg) > 0) {
    type <- "r"
    isTeam <- FALSE
    f <- rankBySkillDfServer("receiver", rv$fds$statistics$player_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("receiver", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("receiver", f, type = type, isTeam = isTeam)
  }
})
```

### Liberos

```{r message=FALSE, warning=FALSE}
rankBySkillUI("libero")
observe({
  if (!is.null(rv$fds$statistics$player_agg) && nrow(rv$fds$statistics$player_agg) > 0) {
    type <- "l"
    isTeam <- FALSE
    f <- rankBySkillDfServer("libero", rv$fds$statistics$player_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("libero", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("libero", f, type = type, isTeam = isTeam)
  }
})
```

# Team Charts

## Row {.tabset}

### Score

```{r message=FALSE, warning=FALSE}
rankBySkillUI("scorer-team")
observe({
  if (!is.null(rv$fds$statistics$team_agg) && nrow(rv$fds$statistics$team_agg) > 0) {
    type <- "c"
    isTeam <- TRUE
    f <- rankBySkillDfServer("scorer-team", rv$fds$statistics$team_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("scorer-team", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("scorer-team", f, type = type, isTeam = isTeam)
  }
})
```

### Score Structure

```{r message=FALSE, warning=FALSE}
rankBySkillUI("structure-team")
observe({
  if (!is.null(rv$fds$statistics$team_agg) && nrow(rv$fds$statistics$team_agg) > 0) {
    type <- "u"
    isTeam <- TRUE
    f <- rankBySkillDfServer("structure-team", rv$fds$statistics$team_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("structure-team", f, type = type, isTeam = isTeam)
  }
})
```

### Attack

```{r message=FALSE, warning=FALSE}
rankBySkillUI("attacker-team")
observe({
  if (!is.null(rv$fds$statistics$team_agg) && nrow(rv$fds$statistics$team_agg) > 0) {
    type <- "a"
    isTeam <- TRUE
    f <- rankBySkillDfServer("attacker-team", rv$fds$statistics$team_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("attacker-team", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("attacker-team", f, type = type, isTeam = isTeam)
  }
})
```

### Block

```{r message=FALSE, warning=FALSE}
rankBySkillUI("blocker-team")
observe({
  if (!is.null(rv$fds$statistics$team_agg) && nrow(rv$fds$statistics$team_agg) > 0) {
    type <- "b"
    isTeam <- TRUE
    f <- rankBySkillDfServer("blocker-team", rv$fds$statistics$team_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("blocker-team", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("blocker-team", f, type = type, isTeam = isTeam)
  }
})
```

### Serve

```{r message=FALSE, warning=FALSE}
rankBySkillUI("server-team")
observe({
  if (!is.null(rv$fds$statistics$team_agg) && nrow(rv$fds$statistics$team_agg) > 0) {
    type <- "s"
    isTeam <- TRUE
    f <- rankBySkillDfServer("server-team", rv$fds$statistics$team_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("server-team", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("server-team", f, type = type, isTeam = isTeam)
  }
})
```

### Dig

```{r message=FALSE, warning=FALSE}
rankBySkillUI("digger-team")
observe({
  if (!is.null(rv$fds$statistics$team_agg) && nrow(rv$fds$statistics$team_agg) > 0) {
    type <- "d"
    isTeam <- TRUE
    f <- rankBySkillDfServer("digger-team", rv$fds$statistics$team_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("digger-team", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("digger-team", f, type = type, isTeam = isTeam)
  }
})
```

### Set

```{r message=FALSE, warning=FALSE}
rankBySkillUI("setter-team")
observe({
  if (!is.null(rv$fds$statistics$team_agg) && nrow(rv$fds$statistics$team_agg) > 0) {
    type <- "e"
    isTeam <- TRUE
    f <- rankBySkillDfServer("setter-team", rv$fds$statistics$team_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("setter-team", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("setter-team", f, type = type, isTeam = isTeam)
  }
})
```

### Receive

```{r message=FALSE, warning=FALSE}
rankBySkillUI("receiver-team")
observe({
  if (!is.null(rv$fds$statistics$team_agg) && nrow(rv$fds$statistics$team_agg) > 0) {
    type <- "r"
    isTeam <- TRUE
    f <- rankBySkillDfServer("receiver-team", rv$fds$statistics$team_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("receiver-team", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("receiver-team", f, type = type, isTeam = isTeam)
  }
})
```

### Team Errors

```{r message=FALSE, warning=FALSE}
rankBySkillUI("error-team")
observe({
  if (!is.null(rv$fds$statistics$team_agg) && nrow(rv$fds$statistics$team_agg) > 0) {
    type <- "f"
    isTeam <- TRUE
    f <- rankBySkillDfServer("error-team", rv$fds$statistics$team_agg, type = type, isTeam = isTeam)
    rankBySkillChartServer("error-team", f, type = type, isTeam = isTeam)
    rankBySkillTableServer("error-team", f, type = type, isTeam = isTeam)
  }
})
```

# Info

## Row {.tabset}

### Schedule

```{r message=FALSE, warning=FALSE}
matchesUI("matches")
observe({
  if (!is.null(rv$ds) && nrow(rv$ds$matches) > 0) {
    matchesServer("matches")
  }
})
```

### P-3
```{r message=FALSE, warning=FALSE}
clipboardP3RUI("matches")
observe({
  if (!is.null(rv$ds) && nrow(rv$ds$matches) > 0) {
    clipboardP3Server("matches")
  }
})
```

### Roster

```{r message=FALSE, warning=FALSE}
rosterUI("roster")
observe({
  if (!is.null(rv$ds) && nrow(rv$ds$players) > 0) {
    rosterServer("roster")
  }
})
```

### Clipboard

```{r message=FALSE, warning=FALSE}
clipboardUI("roster")
observe({
  if (!is.null(rv$ds) && nrow(rv$ds$players) > 0) {
    clipboardServer("roster")
  }
})
```
